---
title: "IRT Parameters for CAT"
author: "George Kachergis & Michael C. Frank"
date: "12/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mirt)
library(mirtCAT)
```

# Production


## English

```{r prod-en}
load("production/eng_ws_wg_mod_2pl_nobad.Rds")
load("production/preferredCAT_eng.Rds")
```

Productive CDI vocabulary of `r nrow(fscores_2pl)` English-speaking children ages 12-36 months used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).

## Spanish

```{r prod-sp}
load("production/sp_ws_wg_mod_2pl_nobad.Rds")
load("production/preferredCAT_sp.Rds")
```

Productive CDI vocabulary of `r nrow(fscores_2pl)` Spanish-speaking children ages 12-30 months used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).


# Comprehension

## English

```{r comp-en}
load("comprehension/eng_wg_mod_2pl_nobad.Rds")
```

Receptive CDI:WG vocabulary of `r nrow(fscores_2pl)` English-speaking children used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).


## Spanish

```{r comp-sp}
load("comprehension/sp_wg_mod_2pl_nobad.Rds")
```

Receptive CDI:WG vocabulary of `r nrow(fscores_2pl)` Spanish-speaking children used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).