---
title: "IRT Parameters for CAT"
author: "George Kachergis & Michael C. Frank"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mirt)
library(mirtCAT)
library(tidyverse)
require(modelr)
require(ggpubr)
```

# Overview

The "mod_2pl" files (for Spanish/English, production/comprehension) each contain a coefs_2pl dataframe of the item parameters (in mirt's slope-intercept form), as well as a mod_2pl mirt model object, and fscores_2pl (the estimated ability parameters from Wordbank participants). 

# Production

## English

```{r prod-en}
it = list() # item parameters
ab = list() # child ability
load("production/eng_ws_wg_mod_2pl_nobad.Rds")
it$en_prod <- coefs_2pl # 680 WS items
ab$en_prod <- fscores_2pl

load("production/preferredCAT_eng.Rds")
```

Productive CDI vocabulary of `r nrow(fscores_2pl)` English-speaking children ages 12-36 months used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).

## Spanish

```{r prod-sp}
load("production/sp_ws_wg_mod_2pl_nobad.Rds")
it$sp_prod <- coefs_2pl
ab$sp_prod <- fscores_2pl

load("production/preferredCAT_sp.Rds")
```

Productive CDI vocabulary of `r nrow(fscores_2pl)` Spanish-speaking children ages 12-30 months used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).


# Comprehension

## English

```{r comp-en}
load("comprehension/eng_wg_mod_2pl.Rds")
it$en_comp <- coefs_2pl
ab$en_comp <- fscores_2pl
```

Receptive CDI:WG vocabulary of `r nrow(fscores_2pl)` English-speaking children used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).


## Spanish

```{r comp-sp}
load("comprehension/sp_wg_mod_2pl.Rds")
it$sp_comp <- coefs_2pl
ab$sp_comp <- fscores_2pl
```

Receptive CDI:WG vocabulary of `r nrow(fscores_2pl)` Spanish-speaking children used to fit a 2PL model with `r nrow(coefs_2pl)` items (after pruning).


# Comprehension vs. Production Item Parameters

How correlated are parameters for comprehension and production?

## Item Difficulty

```{r compare-comp-prod}

en_comp_prod_match <- intersect(it$en_prod$definition, it$en_comp$definition) # 394
setdiff(it$en_comp$definition, it$en_prod$definition) # in and inside


sp_comp_prod_match <- intersect(it$sp_comp$definition, it$sp_prod$definition) # 389
setdiff(it$sp_comp$definition, it$sp_prod$definition) 
# 39 items - can match some of these (e.g., escalera/s, brazo/s, oreja/s...)

all <- it$en_prod %>% 
  mutate(Language = "EN", Task = "Production") %>%
  bind_rows(it$en_comp %>% mutate(Language = "EN", Task = "Comprehension")) %>%
  bind_rows(it$sp_comp %>% mutate(Language = "SP", Task = "Comprehension")) %>%
  bind_rows(it$sp_prod %>% mutate(Language = "SP", Task = "Production"))


all_wide <- all %>% group_by(Language) %>% select(-g, -u) %>%
  pivot_wider(names_from = Task, values_from=c(a1, d))

m_d <- lm(d_Comprehension ~ d_Production*Language, data = all_wide)
m_a1 <- lm(a1_Comprehension ~ a1_Production*Language, data = all_wide)

all_wide <- all_wide %>% add_residuals(m_d) %>%
    rename(d_resid = resid) %>% 
    add_residuals(m_a1) %>%
    rename(a1_resid = resid)

#corrr::correlate(all_wide %>% select(d_Comprehension, d_Production))

```

```{r plot-prod-vs-comp-diff, echo=F, warning=F}
all_wide %>% 
  ggplot(aes(x=d_Production, y=d_Comprehension)) +
  geom_point(alpha=.2) +
  facet_wrap(. ~ Language) + 
  geom_smooth(method='lm') +
  theme_bw() + 
  stat_cor(method = "pearson", label.x = -1, label.y = -8) + 
  ggrepel::geom_label_repel(data = filter(all_wide, abs(d_resid) > 2.1), 
                            aes(label = definition))
```

Strong correlation between comprehension and production item difficulties.
Outliers with easier comprehension than production seem to be mostly verbs.


## Item Discrimination

```{r, echo=F, warning=F}
all_wide %>% 
  ggplot(aes(x=a1_Production, y=a1_Comprehension)) +
  geom_point(alpha=.2) +
  facet_wrap(. ~ Language) + 
  geom_smooth(method='lm') +
  theme_bw() + 
  stat_cor(method = "pearson", label.x = 0, label.y = 1) +
  ggrepel::geom_label_repel(data = filter(all_wide, a1_resid > 1 | a1_resid < -1), 
                            aes(label = definition))
```

# Compare Children's Comprehension vs. Production Ability Estimates

```{r, echo=F, warning=F}
ability <- left_join(ab$en_comp %>% 
                       rename(comp_ability = ability) %>%
                       mutate(Language = "English"), 
                     ab$en_prod %>% 
                       rename(prod_ability = ability) %>%
                       mutate(Language = "English"))
ability <- ability %>% bind_rows(left_join(ab$sp_comp %>%
                          rename(comp_ability = ability) %>%
                          mutate(Language = "Spanish"),
                        ab$sp_prod %>%
                          rename(prod_ability = ability) %>%
                          mutate(Language = "Spanish")))

ability %>% 
  ggplot(aes(x=comp_ability, y=prod_ability)) +
  geom_point(alpha=.2) + xlab("Comprehension Ability") + ylab("Production Ability") +
  facet_wrap(. ~ Language) + 
  geom_smooth(method='lm') +
  theme_bw() + 
  stat_cor(method = "pearson", label.x = 0, label.y = 2.15) 
```

Strong correlations between children's estimated comprehension and production abilities (same or stronger correlation as comprehension vs. production sumscores?).

# Predicting Total Vocabulary Size from Ability

Fit GLM to predict vocabulary size from IRT ability (and age and sex?).

```{r, echo=F}
demo <- list()
load("data/wordbank_eng_wg_webcdi.Rds")
demo$en_comp <- d_demo %>% mutate(Language = "English")
load("data/wordbank_eng_ws_wg_webcdi31-36mos.Rds")
demo$en_prod <- d_demo %>% mutate(Language = "English")

load("data/wordbank_sp_wg_webcdi.Rds")
demo$sp_comp <- d_demo %>% mutate(Language = "Spanish")
load("data/wordbank_sp_ws_wg_webcdi12-30mos.Rds")
demo$sp_prod <- d_demo %>% mutate(Language = "Spanish")

demo$en_comp <- demo$en_comp %>% left_join(ab$en_comp %>% type_convert())
demo$sp_comp <- demo$sp_comp %>% left_join(ab$sp_comp %>% type_convert())

demo$en_prod <- demo$en_prod %>% left_join(ab$en_prod %>% type_convert())
demo$sp_prod <- demo$sp_prod %>% left_join(ab$sp_prod %>% type_convert())

#ability <- ability %>% 
#  type_convert() %>%
#  left_join(demo$en_comp) %>%
#  left_join(demo$en_prod) %>%
#  left_join(demo$sp_comp) %>%
#  left_join(demo$sp_prod)
# some NAs in production for some reason...

```


```{r}
en_comp <- lm(comprehension ~ age + sex + ability, 
                       data=demo$en_comp)
summary(en_comp)

en_prod <- lm(production ~ age + sex + ability, 
                       data=demo$en_prod)
summary(en_prod)
# cor(demo$en_comp$comprehension, demo$en_comp$ability) # .96
# cor(demo$en_comp$age, demo$en_comp$ability) # .62
```


# Preferred CAT Settings

The above item parameters can be used to run a CAT, for example with the mirtCAT package. 
Based on real data simulations, we recommend a minimum of 25 items, a maximum of 50, with termination at SE = .15, and ML scoring.
In the below call, the maximally-informative (MI) start item is chosen, but we can instead supply an age-based starting item (based on mean theta for each age) if you can use that.

```{r cat-settings, eval=F}
mirtCAT(mo = mod_2pl, criteria = 'MI', start_item = 'MI', 
                     method = 'ML', cl = cl, #local_pattern = dat, 
                     design = list(min_items = 25,
                                   max_items = 50, 
                                   min_SEM = 0.15))
```

